Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 appendix.tex
Appendix Figure 8 and partial Figure 5

@@

@@

>>>>

Replicability:

\begin{enumerate}
    \item
\end{enumerate}

@@

Correlation between backfill availability of cores and walltime on Titan during the experiment time window.

\begin{itemize}
    \item Raw data: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_5/titan_backfill_availability.txt}, as provided by the PanDA Brokers logs on Titan.
    \item Wrangling: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_5/titan_backfill_availability.csv}
    \item Analysis and Plotting: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_5/titan_backfill_availability.ipynb}
\end{itemize}

Replicability:

\begin{enumerate}
    \item
\end{enumerate}

@@

Panda failures on Titan by exit code during the experiment window.

\begin{itemize}
    \item Raw data: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_8/panda-broker-failures_jan2016-feb2017.csv}
    \item Wrangling: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_8/panda-broker-failures_jan2016-feb2017.xlsx} (Pivot Data \& Wrangled Data tabs)
    \item Analysis: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_8/panda-broker-failures_jan2016-feb2017.xlsx} (Aggregated Data tab)
    \item Plotting: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_8/panda-broker-failures_jan2016-feb2017.xlsx} (Plots tab)
\end{itemize}

Replicability:

\begin{enumerate}
    \item Download raw data download in csv format from the ATLAS jobs dashboard. Download link: \url{http://dashb-atlas-job.cern.ch/dashboard/request.py/terminatedjobsstatuscsv?sites=All%20T3210&sitesCat=All%20Countries&resourcetype=All&pandares=ORNL_Titan_MCORE&activities=simul&sitesSort=7&sitesCatSort=0&start=2016-01-01&end=2017-02-28&timeRange=daily&sortBy=16&granularity=Monthly&generic=0&series=30&type=abcb}
    \item Load the csv file into Excel (or any other software/language).
    \item Create a pivot table with failure types as columns and months as rows.
    \item Aggregate data of error codes of the same type by merge columns and adding the values of their raws according to this table:
    \item Plot the resulting table as a stacked area diagram.
\end{enumerate}
